Mallows, Black-box combinatorial optimization, limited budget, ???

### 2020-09-10 paper/main.tex
save function evaluations explicitly.
import numpy

In many practical optimization problems, the objective function is not
explicitly available and solutions are evaluated by means of expensive
prediction models, simulations or physical experiments. When decision variables
are continuous, the use of Bayesian surrogate-models, e.g., Gaussian processes,
in optimization has become widespread~\citep{JonSchWel98go,ForKea2009surrogate}. Motivated by this success, there have been attempts at adapting such surrogate models to the combinatorial case~\citep{ZaeStoBar2014:ppsn,ZaeStoFriFisNauBar2014},

>>>>

In many practical optimization problems, the objective function is not
explicitly available and solutions are evaluated by means of expensive
prediction models, simulations or physical experiments. When decision variables
are continuous, the use of Bayesian surrogate-models, e.g., Gaussian processes,
in optimization has become
widespread~\citep{JonSchWel98go,ForKea2009surrogate}. Motivated by this
success, there have been attempts at adapting such surrogate models to the
combinatorial case~\citep{ZaeStoBar2014:ppsn,ZaeStoFriFisNauBar2014}.
